### 2017-03-03 Theory/Theory.tex
Own final read through

%Particles that carry electric charge interact via the
%electromagnetic force, while the weak force works
%between particles carrying weak isospin.
%The weak force, which interacts with all fermions,
%only couples to the left-handed part of fermion states. In 
%A general fermion state $\chi$ can be decomposed into its left- and right-handed parts
%\begin{equation}\label{eqn:leftright}
%\chi=\psi_R+\psi_L.
%\end{equation}
%The weak force only couples to $\psi_L$, and is thus violates parity maximally.
%where only $\psi_L$ will interact via the weak force. %For massless particles
%the general state $\chi$ is not a mixture of left-handed and right-handed parts,
%but is either completely left-handed or right-handed. As such neutrinos, which are
%massless in the \ac{SM}, must all be left-handed. %CAREFUL: handedness =/= helicity
%The observation of neutrino flavour oscillations since the formulation of
%the \ac{SM} implies that neutrinos do have a small but finite mass
%and so there must be right-handed neutrinos in the \ac{SM}. This will
%not be discussed here, for a more detailed account see reference \cite{pdg-2014}.
%The weak isospin acts on doublets of left-handed lepton pairs, while
%the right-handed leptons transform as singlet states. This works similarly
%for the quarks, with weak isospin acting three left-handed doublets and
%Another feature of the weak force is that the weak eigenstates of the quarks
%differ from the physical states, which mix via the \ac{CKM}-matrix \cite{ckm-matrix-cabibbo,ckm-matrix-KM}
%in charged current interactions as
%\begin{equation}\label{eqn:ckm_matrix}
%\begin{pmatrix} d' \\
%s' \\
%b'  \end{pmatrix} = \begin{pmatrix} V_{ud} & V_{us} & V_{ub} \\
%V_{cd} & V_{cs} & V_{cb} \\
%V_{td} & V_{ts} & V_{tb} \end{pmatrix} \begin{pmatrix} d \\
%s\\
%b \end{pmatrix}.
%\end{equation}
The SU(2) part of the symmetry is built from the weak
isospin generators $I_{1,2,3} = \frac{1}{2}\sigma_{1,2,3}$,
where $\sigma_i$ are the Pauli spin matrices. The U(1)
symmetry comes from the weak hypercharge generator $Y$, which
is related to weak isospin and electric charge as
\begin{equation}\label{eqn:hypercharge}
Q = I_3 + \frac{1}{2}Y.
\end{equation}
The associated gauge fields are the three weak isospin fields $\PW_{\mu}^{i}$ and the
weak hypercharge field $\text{B}_{\mu}$. These four fields mix to form the physical \Pphoton,
\PZ and $\PW^{\pm}$ states as
\begin{equation}\label{eqn:ewk_propagators_W}
\PW_{\mu}^{\pm} &= \frac{1}{\sqrt{2}}(\PW_{\mu}^1 \mp i \PW_{\mu}^2),
\end{equation}
\begin{equation}\label{eqn:ewk_propagators_phot}
\text{A}_{\mu} &= \PW_{\mu}^3\sin{\theta_W} + \text{B}_{\mu}\cos{\theta_W},
\end{equation}
\begin{equation}\label{eqn:ewk_propagators_Z}
\PZ_{\mu} &= \PW_{\mu}^3\cos{\theta_W} - \text{B}_{\mu}\sin{\theta_W}.
\end{equation}
In these equations $\text{A}_{\mu}$ is the photon field and $\PZ_{\mu}$ the \PZ field.
The weak mixing angle $\theta_W$ is related to the weak ($g$) and electromagnetic ($g'$)
coupling constants as
\begin{equation}\label{eqn:thetaw}
\begin{split}
g\sin{\theta_W} &= g'\cos{\theta_W}\\
\Rightarrow \sin{\theta_W} &= \frac{g'}{\sqrt{g^2+g'^2}} \text{ and } \cos{\theta_W} = \frac{g}{\sqrt{g^2+g'^2}}.
\end{split}
\end{equation}
Neutral weak-current interactions were discovered in 1973 at the Gargamelle
bubble chamber experiment at \acs{CERN} \cite{gargamelle}. This discovery was 
followed ten years later by the discovery of the $\PW^{\pm}$ \cite{UA1-1,UA2-1} and $\PZ$ \cite{UA1-2,UA2-2} bosons by the UA1
and UA2 Collaborations at \acs{CERN}, confirming the predictions from electroweak unification.
It should be noted that the weak force only couples to the left-handed parts
of fermion states, and so is maximally parity violating.

@@

\section{Standard model Higgs boson measurements}
\label{sec:theory_smH}
The mass of the Higgs boson is a free parameter in the \ac{SM}, and so
a large range of possible masses needed to be covered in Higgs boson searches. 
Searches for the Higgs boson at the \ac{LEP} collider did not lead
to its observation. However, masses below $114.4\,\GeV$ were excluded at the 95\% \ac{CL} \cite{LEP-Higgs},
providing a lower search limit. Subsequent searches at the 
Tevatron also did not lead to the discovery of the Higgs boson, but did exclude 
an additional mass range of $140$--$186\,\GeV$ at the 95\% \ac{CL} \cite{TEV-Higgs}.

@@

m_{\PHiggs,\PHiggslight}^2 = \frac{1}{2}[m_{\PHiggsps}^2+m_{\PZ}^2 \pm \sqrt{(m_{\PHiggsps}^2+m_{\PZ}^2)^2-4m_{\PZ}^2m_{\PHiggsps}^2\text{cos}^2 2\beta}].

@@

Figure \ref{fig:mhmodp_br} shows the branching ratio of the \PHiggs and \PHiggsps 
into $\tau\tau$. The branching ratios into $\tau\tau$ are enhanced, especially at
high \tanb, showing how this decay channel is useful for MSSM Higgs boson searches.

@@

\subsection{MSSM scenarios at low \tanb}
\label{sec:mssm_theory_lowtb}
The mass of the light Higgs boson in the \ac{MSSM} is said to
be compatible with $125\,\GeV$ if the light Higgs boson mass lies within 
$\pm 3\,\GeV$ of $125\,\GeV$. This mass window
corresponds to the theoretical uncertainty on the \ac{MSSM} prediction for \mh.
A large area of the \mA-\tanb~plane in the $m_{\PHiggslight}^{\text{mod+}}$ 
scenario contains a light Higgs boson with a mass compatible with
$125\,\GeV$. However, at low values of \tanb~this is not the case.
This is illustrated in figure \ref{fig:mhmodp_mh}a, where the mass of the light Higgs
boson in the $m_{\PHiggslight}^{\text{mod}+}$ scenario is shown.
The low \tanb~regime can be re-opened
if $M_{\text{SUSY}}$ is allowed to be greater than $3\,\TeV$ \cite{MSSM-reopen}. 
%But not too large, see ref above!
%Figure \ref{fig:tanb_accessibility} shows contours of constant
%light Higgs boson mass as a function of \tanb~and $M_{\text{SUSY}}$.
%It indicates that values of \mh~can be compatible with 125$\pm$3 GeV
%for \tanb~values down to 1 if $M_{\text{SUSY}}$ is around 100-1000 TeV. 
%\tanb~values of 3-5 are even accessible for $M_{\text{SUSY}}$ of around 10 TeV.
%
%\begin{figure}[h!]
%\begin{center}
%\includegraphics[width=0.5\textwidth]{./Theory/Figures/tanb_accessibility.png}
%\end{center}
%\caption{Contours of constant light Higgs boson mass as a function of \tanb~and $M_{\text{SUSY}}$.
%High values of $M_{\text{SUSY}}$ allow for light Higgs boson masses compatible with
%125 GeV down to low values of \tanb~\cite{hMSSM-2}.}
%\label{fig:tanb_accessibility}
%\end{figure}
%where the ±3 GeV variation corresponds to a rough estimate of the theoretical uncertainty of the MSSM prediction for mh, due to the unknown effect of higher-order correction

@@

\subsubsection{The low-\tanb~scenario}
\label{sec:theory_BSM_model_lowtb}
In the low-\tanb~scenario \cite{Hein-low-tb-high,MSSM-lowtanb}, the SUSY parameters entering
the radiative corrections are tuned to obtain a light 
Higgs boson mass of around $125\,\GeV$ in most of the \mA-\tanb~plane considered.
Figure \ref{fig:mhmodp_mh}b shows that, apart from in a corner of \tanb~$=1$--$4$ and 
\mA~$=150$--$250\,\GeV$, \mh~is compatible with $125\,\GeV$.

\begin{figure}[h!]
\begin{center}
\subfloat[$m_{\PHiggslight}^{\text{mod}+}$ scenario]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/mh_mhmodp.pdf}}
\subfloat[Low-\tanb~scenario]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/mh_lowtbhigh.pdf}}
\end{center}
\caption[The mass of the light Higgs boson, \mh, as a function of \mA~and
\tanb~in the $m_{\PHiggslight}^{\text{mod+}}$ scenario and the low-\tanb~scenario.]{The mass of the light Higgs boson, \mh, as a function 
of \mA~and \tanb~in (a) the $m_{\PHiggslight}^{\text{mod+}}$ scenario and (b) the low-\tanb~scenario. The white areas
indicate masses lower than $122\,\GeV$. The figures show that
the mass of the light Higgs boson is compatible with $125\,\GeV$ over a large
part of the \mA-\tanb~plane in the $m_{\PHiggslight}^{\text{mod+}}$ scenario, except at low \tanb. In the low-\tanb~scenario
the mass of the light Higgs boson is compatible with $125\,\GeV$ nearly everywhere. These values are based on the calculations in reference \cite{YR3}.}
\label{fig:mhmodp_mh}
\end{figure}
%\begin{figure}[h!]
%\begin{center}
%\includegraphics[width=0.5\textwidth]{./Theory/Figures/mh_lowtbhigh.png}
%\end{center}
%\caption{Mass of the light Higgs boson in the \mA-\tanb~plane of the low-\tanb~scenario.
%The mass is compatible with $125\,\GeV$ nearly everywhere \cite{MSSM-lowtanb}.}
%\label{fig:lowtbhigh_mh}
%\end{figure}
To obtain \mh~$\approx125\,\GeV$ over a large part of the parameter
space, 
$M_{\text{SUSY}}$ is not fixed but varies between a few $\TeV$ and $100\,\TeV$, while
varying the parameter $X_{\Ptop}$ as:
\begin{equation}
\begin{split}
\tan{\beta} \leq 2 &: \frac{X_{\Ptop}}{M_{\text{SUSY}}} = 2,\\
2 < \tan{\beta} \leq 8.6 &: \frac{X_{\Ptop}}{M_{\text{SUSY}}} = 0.0375\text{tan}^2\beta - 0.7\tan{\beta} + 3.25,\\
8.6 < \tan{\beta} &: \frac{X_{\Ptop}}{M_{\text{SUSY}}} = 0.
\end{split}
\end{equation}
The other trilinear couplings are set to $2\,\TeV$, with $\mu_{\text{MSSM}}$ set to $1.5\,\TeV$ and $M_2$ to $2\,\TeV$.

@@

\section{Status of BSM Higgs boson searches}
\label{sec:theory_BSMH_status}
With the data collected by the \ac{LHC}
experiments up to the end of 2012 many searches for \ac{BSM} Higgs
bosons were performed. Figure \ref{fig:bsm_summary} shows the interpetations
of different searches performed with the \acs{CMS} detector during this period
in the $m_{\PHiggslight}^{\text{mod+}}$ (figure~\ref{fig:bsm_summary}a)
and hMSSM (figure~\ref{fig:bsm_summary}b) scenarios. The direct search for heavier Higgs bosons decaying into pairs
of tau leptons sets the most stringent limits at high \tanb, with searches for 
heavy Higgs bosons decaying to $\Pbottom\Pbottom$ and to $\mu\mu$ both excluding smaller parts of the high-\tanb~region.
Searches for heavy Higgs bosons decaying to $\PW\PW$ and $\PZ\PZ$ are able to exclude part of the low-\tanb~region. In the 
hMSSM scenario searches for \Htohh and \AtoZh can exclude a small area at low \tanb~and between \mA~$=250$--$350\,\GeV$.
The red exclusion contour in figure \ref{fig:bsm_summary}b is the reinterpretation of the analysis presented in
chapter \ref{chap:hhh}.

>>>>

%Particles that carry electric charge interact via the
%electromagnetic force, while the weak force works
%between particles carrying weak isospin.
%The weak force, which interacts with all fermions,
%only couples to the left-handed part of fermion states. In 
%A general fermion state $\chi$ can be decomposed into its left- and right-handed parts
%\begin{equation}\label{eqn:leftright}
%\chi=\psi_R+\psi_L.
%\end{equation}
%The weak force only couples to $\psi_L$, and is thus violates parity maximally.
%where only $\psi_L$ will interact via the weak force. %For massless particles
%the general state $\chi$ is not a mixture of left-handed and right-handed parts,
%but is either completely left-handed or right-handed. As such neutrinos, which are
%massless in the \ac{SM}, must all be left-handed. %CAREFUL: handedness =/= helicity
%The observation of neutrino flavour oscillations since the formulation of
%the \ac{SM} implies that neutrinos do have a small but finite mass
%and so there must be right-handed neutrinos in the \ac{SM}. This will
%not be discussed here, for a more detailed account see reference \cite{pdg-2014}.
%The weak isospin acts on doublets of left-handed lepton pairs, while
%the right-handed leptons transform as singlet states. This works similarly
%for the quarks, with weak isospin acting three left-handed doublets and
%Another feature of the weak force is that the weak eigenstates of the quarks
%differ from the physical states, which mix via the \ac{CKM}-matrix \cite{ckm-matrix-cabibbo,ckm-matrix-KM}
%in charged current interactions as
%\begin{equation}\label{eqn:ckm_matrix}
%\begin{pmatrix} d' \\
%s' \\
%b'  \end{pmatrix} = \begin{pmatrix} V_{ud} & V_{us} & V_{ub} \\
%V_{cd} & V_{cs} & V_{cb} \\
%V_{td} & V_{ts} & V_{tb} \end{pmatrix} \begin{pmatrix} d \\
%s\\
%b \end{pmatrix}.
%\end{equation}
The SU(2) part of the symmetry is built from the weak
isospin generators \mbox{$I_{1,2,3} = \frac{1}{2}\sigma_{1,2,3}$},
where $\sigma_i$ are the Pauli spin matrices. The U(1)
symmetry comes from the weak hypercharge generator $Y$, which
is related to weak isospin and electric charge as
\begin{equation}\label{eqn:hypercharge}
Q = I_3 + \frac{1}{2}Y.
\end{equation}
The associated gauge fields are the three weak isospin fields $\PW_{\mu}^{i}$ and the
weak hypercharge field $\text{B}_{\mu}$. These four fields mix to form the physical \Pphoton,
\PZ and $\PW^{\pm}$ states as
\begin{equation}\label{eqn:ewk_propagators_W}
\PW_{\mu}^{\pm} &= \frac{1}{\sqrt{2}}(\PW_{\mu}^1 \mp i \PW_{\mu}^2),
\end{equation}
\begin{equation}\label{eqn:ewk_propagators_phot}
\text{A}_{\mu} &= \PW_{\mu}^3\sin{\theta_W} + \text{B}_{\mu}\cos{\theta_W},
\end{equation}
\begin{equation}\label{eqn:ewk_propagators_Z}
\PZ_{\mu} &= \PW_{\mu}^3\cos{\theta_W} - \text{B}_{\mu}\sin{\theta_W}.
\end{equation}
In these equations $\text{A}_{\mu}$ is the photon field and $\PZ_{\mu}$ the \PZ field.
The weak mixing angle $\theta_W$ is related to the weak ($g$) and electromagnetic ($g'$)
coupling constants as
\begin{equation}\label{eqn:thetaw}
\begin{split}
g\sin{\theta_W} &= g'\cos{\theta_W}\\
\Rightarrow \sin{\theta_W} &= \frac{g'}{\sqrt{g^2+g'^2}} \text{ and } \cos{\theta_W} = \frac{g}{\sqrt{g^2+g'^2}}.
\end{split}
\end{equation}
Neutral weak-current interactions were discovered in 1973 at the Gargamelle
bubble chamber experiment at \acs{CERN} \cite{gargamelle}. This discovery was 
followed ten years later by the discovery of the $\PW^{\pm}$ \cite{UA1-1,UA2-1} and $\PZ$ \cite{UA1-2,UA2-2} bosons by the UA1
and UA2 Collaborations at \acs{CERN}, confirming the predictions from electroweak unification.
It should be noted that the weak force only couples to the left-handed parts
of fermion states, and so is maximally parity violating.

@@

\section{Standard model Higgs boson measurements}
\label{sec:theory_smH}
The mass of the Higgs boson is a free parameter in the \ac{SM}, and so
a large range of possible masses needed to be covered in Higgs boson searches. 
Searches for the Higgs boson at the \ac{LEP} collider did not lead
to its observation. However, masses below $114.4\,\GeV$ were excluded at the 95\% \ac{CL} \cite{LEP-Higgs},
providing a lower search limit. Subsequent searches at the 
Tevatron also did not lead to the discovery of the Higgs boson, but did exclude 
an additional mass range of $140$--$186\,\GeV$ at the \mbox{95\% \ac{CL} \cite{TEV-Higgs}}.

@@

m_{\PHiggs,\PHiggslight}^2 = \frac{1}{2}[m_{\PHiggsps}^2+m_{\PZ}^2 \pm \sqrt{(m_{\PHiggsps}^2+m_{\PZ}^2)^2-4m_{\PZ}^2m_{\PHiggsps}^2\text{cos}^2 2\beta}~].

@@

Figure \ref{fig:mhmodp_br} shows the branching ratios of the \PHiggs and \PHiggsps 
bosons into $\tau\tau$. The branching ratios into $\tau\tau$ are enhanced, especially at
high \tanb, showing how this decay channel is useful for MSSM Higgs boson searches.

@@

\subsection{MSSM scenarios at low \tanb}
\label{sec:mssm_theory_lowtb}
The mass of the light Higgs boson in the \ac{MSSM} is said to
be compatible with $125\,\GeV$ if the light Higgs boson mass lies within 
$\pm 3\,\GeV$ of $125\,\GeV$. This mass window
corresponds to the theoretical uncertainty on the \ac{MSSM} prediction for \mh.
A large area of the \mbox{\mA-\tanb}~plane in the $m_{\PHiggslight}^{\text{mod+}}$ 
scenario contains a light Higgs boson with a mass compatible with
$125\,\GeV$. However, at low values of \tanb~this is not the case.
This is illustrated in figure \ref{fig:mhmodp_mh}a, where the mass of the light Higgs
boson in the $m_{\PHiggslight}^{\text{mod}+}$ scenario is shown.
The low \tanb~regime can be re-opened
if $M_{\text{SUSY}}$ is allowed to be greater than $3\,\TeV$ \cite{MSSM-reopen}. 
%But not too large, see ref above!
%Figure \ref{fig:tanb_accessibility} shows contours of constant
%light Higgs boson mass as a function of \tanb~and $M_{\text{SUSY}}$.
%It indicates that values of \mh~can be compatible with 125$\pm$3 GeV
%for \tanb~values down to 1 if $M_{\text{SUSY}}$ is around 100-1000 TeV. 
%\tanb~values of 3-5 are even accessible for $M_{\text{SUSY}}$ of around 10 TeV.
%
%\begin{figure}[h!]
%\begin{center}
%\includegraphics[width=0.5\textwidth]{./Theory/Figures/tanb_accessibility.png}
%\end{center}
%\caption{Contours of constant light Higgs boson mass as a function of \tanb~and $M_{\text{SUSY}}$.
%High values of $M_{\text{SUSY}}$ allow for light Higgs boson masses compatible with
%125 GeV down to low values of \tanb~\cite{hMSSM-2}.}
%\label{fig:tanb_accessibility}
%\end{figure}
%where the ±3 GeV variation corresponds to a rough estimate of the theoretical uncertainty of the MSSM prediction for mh, due to the unknown effect of higher-order correction

@@

\begin{figure}[h!]
\begin{center}
\subfloat[$m_{\PHiggslight}^{\text{mod}+}$ scenario]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/mh_mhmodp.pdf}}
\subfloat[Low-\tanb~scenario]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/mh_lowtbhigh.pdf}}
\end{center}
\caption[The mass of the light Higgs boson, \mh, as a function of \mA~and
\tanb~in the $m_{\PHiggslight}^{\text{mod+}}$ scenario and the low-\tanb~scenario.]{The mass of the light Higgs boson, \mh, as a function 
of \mA~and \tanb~in (a) the $m_{\PHiggslight}^{\text{mod+}}$ scenario and (b) the low-\tanb~scenario. The white areas
indicate masses lower than $122\,\GeV$. The figures show that
the mass of the light Higgs boson is compatible with $125\,\GeV$ over a large
part of the \mA-\tanb~plane in the $m_{\PHiggslight}^{\text{mod+}}$ scenario, except at low \tanb. In the low-\tanb~scenario
the mass of the light Higgs boson is compatible with $125\,\GeV$ nearly everywhere. These values are based on the calculations in reference \cite{YR3}.}
\label{fig:mhmodp_mh}
\end{figure}

\subsubsection{The low-\tanb~scenario}
\label{sec:theory_BSM_model_lowtb}
In the low-\tanb~scenario \cite{Hein-low-tb-high,MSSM-lowtanb}, the SUSY parameters entering
the radiative corrections are tuned to obtain a light 
Higgs boson mass of around $125\,\GeV$ in most of the \mbox{\mA-\tanb}~plane considered.
Figure \ref{fig:mhmodp_mh}b shows that, apart from in a corner of \tanb~$=1$--$4$ and 
\mA~$=150$--$250\,\GeV$, \mh~is compatible with $125\,\GeV$.

%\begin{figure}[h!]
%\begin{center}
%\includegraphics[width=0.5\textwidth]{./Theory/Figures/mh_lowtbhigh.png}
%\end{center}
%\caption{Mass of the light Higgs boson in the \mA-\tanb~plane of the low-\tanb~scenario.
%The mass is compatible with $125\,\GeV$ nearly everywhere \cite{MSSM-lowtanb}.}
%\label{fig:lowtbhigh_mh}
%\end{figure}
To obtain \mh~$\approx125\,\GeV$ over a large part of the parameter
space, 
$M_{\text{SUSY}}$ is not fixed but varies between a few $\TeV$ and $100\,\TeV$, while
varying the parameter $X_{\Ptop}$ as:
\begin{equation}
\begin{split}
\tan{\beta} \leq 2 &: \frac{X_{\Ptop}}{M_{\text{SUSY}}} = 2,\\
2 < \tan{\beta} \leq 8.6 &: \frac{X_{\Ptop}}{M_{\text{SUSY}}} = 0.0375\text{tan}^2\beta - 0.7\tan{\beta} + 3.25,\\
8.6 < \tan{\beta} &: \frac{X_{\Ptop}}{M_{\text{SUSY}}} = 0.
\end{split}
\end{equation}
The other trilinear couplings are set to $2\,\TeV$, with $\mu_{\text{MSSM}}$ set to $1.5\,\TeV$ and $M_2$ to $2\,\TeV$.

@@

\section{Status of BSM Higgs boson searches}
\label{sec:theory_BSMH_status}
With the data collected by the \ac{LHC}
experiments up to the end of 2012 many searches for \ac{BSM} Higgs
bosons were performed. Figure \ref{fig:bsm_summary} shows the interpretations
of different searches performed with the \acs{CMS} detector during this period
in the $m_{\PHiggslight}^{\text{mod+}}$ (figure~\ref{fig:bsm_summary}a)
and hMSSM (figure~\ref{fig:bsm_summary}b) scenarios. The direct search for heavier Higgs bosons decaying into pairs
of tau leptons sets the most stringent limits at high \tanb, with searches for 
heavy Higgs bosons decaying to $\Pbottom\Pbottom$ and to $\mu\mu$ both excluding smaller parts of the high-\tanb~region.
Searches for heavy Higgs bosons decaying to $\PW\PW$ and $\PZ\PZ$ are able to exclude part of the low-\tanb~region. In the 
hMSSM scenario searches for \Htohh and \AtoZh can exclude a small area at low \tanb~and between \mA~$=250$--$350\,\GeV$.
The red exclusion contour in figure \ref{fig:bsm_summary}b is the reinterpretation of the analysis presented in
chapter \ref{chap:hhh}.

### 2017-03-03 frontmatter.tex
A few more minor changes before sending off to supervisors
Own final read through

% Abstract
\begin{abstract}%[\smaller \thetitle\\ \vspace*{1cm} \smaller {\theauthor}]
  %\thispagestyle{empty}
The Compact Muon Solenoid (CMS) detector is a general-purpose detector located at the Large Hadron
Collider at CERN. It was designed to test the predictions of the standard model 
and to search for the Higgs boson in addition to searches for new physics beyond
the standard model.
The analyses presented in this thesis are searches for neutral
Higgs bosons with tau leptons in the final state. These searches use proton-proton collision data recorded
by CMS during 2012, 2015 and 2016. The searches are performed in the
context of the minimal supersymmetric standard model (MSSM). One of the analyses, using $19.7\,\invfb$ 
of data collected
during 2012 at $\sqrt{s}=8\,\TeV$, is a search for a heavy neutral Higgs boson
decaying into two $125\,\GeV$ Higgs bosons with standard model-like properties,
with two b-quarks and two tau leptons in the final state. The other analyses use 
$2.3\,\invfb$ of data collected during 2015 and $12.9\,\invfb$ of data collected during 2016, both
at $\sqrt{s}=13\,\TeV$. These are searches for neutral MSSM
Higgs bosons in the mass range of \mbox{$90\,\GeV$--$3.2\,\TeV$} directly decaying
into pairs of tau leptons. 
No significant excess is observed in any of the searches. Upper limits at the 95\% confidence 
level are set on the cross section times branching ratio for the production of Higgs bosons in the MSSM.
In addition, limits are set in the \mA-\tanb~parameter space of 
several MSSM benchmark scenarios, and in the \cosba-\tanb~parameter space of 
a two Higgs doublet model.

@@

% Declaration
\begin{declaration}
  \vspace*{1cm}
  I declare that the work in this thesis is mine. Figures and results taken from other sources
include the appropriate reference in the text or figure caption. Figures labelled `CMS' are sourced
directly from CMS publications. The `CMS Preliminary' label indicates figures which
have been made public via a preliminary public document or a public website, but are not
included in a publication in a peer-reviewed journal. Figures labelled `CMS' or `CMS preliminary', 
including those made by myself, include the relevant reference in the figure caption.
The work for the analyses presented in chapters \ref{chap:hhh} and \ref{chap:mssm} was 
carried out as part of the CMS \Htotautau working group, and in collaboration with other members of the group.
For the results presented in chapter \ref{chap:hhh} I contributed to the data analysis of two out of three
final states presented in the final public result, and I 
was responsible for the statistical inference. This included
the interpretation of the results in MSSM and 2HDM benchmark scenarios. The 
work is included in reference \cite{CMS-HIG-14-034}. For the results presented in chapter \ref{chap:mssm}
I was responsible for all stages of the analysis, including the optimisation
of object selection and event categorisation, as well as studies of background
methods for three out of four channels in the public result of the analysis,
evaluation of systematic uncertainties in all four channels, and production of the statistical
results, including model interpretations. This work is included in the most recent
preliminary result \cite{CMS-PAS-HIG-16-037}, as well as a predating preliminary
result using a smaller dataset \cite{CMS-PAS-HIG-16-006}.
The work presented in chapter \ref{sec:mssm_combination} has
not been made public, and draws on the results of \cite{CMS-PAS-HIG-16-037} and \cite{CMS-PAS-HIG-16-006}.

@@

%% Strictly optional!
%% I don't want a page number on the following blank page either.
\thispagestyle{empty}

>>>>

% Abstract
\begin{abstract}%[\smaller \thetitle\\ \vspace*{1cm} \smaller {\theauthor}]
  %\thispagestyle{empty}
The Compact Muon Solenoid (CMS) detector is a general-purpose detector located at the Large Hadron
Collider at CERN. It was designed to test the predictions of the standard model 
and to search for the Higgs boson in addition to searches for new physics beyond
the standard model.
The analyses presented in this thesis are searches for neutral
Higgs bosons with tau leptons in the final state. These searches use proton-proton collision data recorded
by CMS during 2012, 2015 and 2016. The searches are performed in the
context of the minimal supersymmetric standard model (MSSM). One of the analyses, using $19.7\,\invfb$ 
of data collected
during 2012 at $\sqrt{s}=8\,\TeV$, is a search for a heavy neutral Higgs boson
decaying into two $125\,\GeV$ Higgs bosons with standard model-like properties,
with two b-quarks and two tau leptons in the final state. The other analyses use 
$2.3\,\invfb$ of data collected during 2015 and $12.9\,\invfb$ of data collected during 2016, both
at $\sqrt{s}=13\,\TeV$. These are searches for neutral MSSM
Higgs bosons in the mass range of \mbox{$90\,\GeV$--$3.2\,\TeV$} directly decaying
into pairs of tau leptons. 
No significant excess is observed in any of the searches. Upper limits at the 95\% confidence 
level are set on the cross section times branching ratio for the production of Higgs bosons in the MSSM.
In addition, limits are set in the \mbox{\mA-\tanb}~parameter space of 
several MSSM benchmark scenarios, and in the \mbox{\cosba-\tanb}~parameter space of 
a two Higgs doublet model.

@@

% Declaration
\begin{declaration}
  \vspace*{1cm}
  I declare that the work in this thesis is mine. Figures and results taken from other sources
include the appropriate reference in the text or figure caption. Figures labelled `CMS' are sourced
directly from CMS publications. The `CMS Preliminary' label indicates figures which
have been made public via a preliminary public document or a public website, but are not
included in a publication in a peer-reviewed journal. Figures labelled `CMS' or `CMS preliminary', 
including those made by myself, include the relevant reference in the figure caption.
The work for the analyses presented in chapters~\ref{chap:hhh} and \ref{chap:mssm} was 
carried out as part of the CMS \Htotautau working group, and in collaboration with other members of the group.
For the results presented in chapter \ref{chap:hhh} I contributed to the data analysis of two out of three
final states presented in the final public result, and I 
was responsible for the statistical inference. This included
the interpretation of the results in MSSM and 2HDM benchmark scenarios. The 
work is included in reference \cite{CMS-HIG-14-034}. For the results presented in chapter~\ref{chap:mssm}
I was responsible for all stages of the analysis, including the optimisation
of object selection and event categorisation, as well as studies of background
methods for three out of four channels in the public result of the analysis,
evaluation of systematic uncertainties in all four channels, and production of the statistical
results, including model interpretations. This work is included in the most recent
preliminary result \cite{CMS-PAS-HIG-16-037}, as well as a predating preliminary
result using a smaller dataset \cite{CMS-PAS-HIG-16-006}.
The work presented in chapter~\ref{sec:mssm_combination} has
not been made public, and draws on the results of \cite{CMS-PAS-HIG-16-037} and \cite{CMS-PAS-HIG-16-006}.

@@

%% Strictly optional!
%% I don't want a page number on the following blank page either.
%\thispagestyle{empty}
